A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Electron Beam Dynamics

### 2018-09-28 paper/prab.tex
first round of edits with Dr. Neveu
typo

%\noindent\begin{minipage}{0.48\textwidth}
%\noindent
\begin{code}[Assembling the optimizer \\ from components]
typedef  \textsc{OPAL-t} InputFileParser Input_t;
typedef PisaVariator        Opt_t;
typedef OpalSimulation      Sim_t;

@@

>>>>

%\noindent\begin{minipage}{0.48\textwidth}
%\noindent
\begin{code}[Assembling the optimizer \\ from components]
typedef InputFileParser Input_t;
typedef PisaVariator        Opt_t;
typedef OpalSimulation      Sim_t;

@@

Outlook, ....
